---
title: "CDS-101 Final Project"
author: 
  - Eunho Cha, Daeun Choi, Songlee Jun, Hyun Woo Kang
  - Dawon Kyoung, Byungwook Oh, Duy Tran
date: "`r Sys.Date()`"
documentclass: article
geometry: margin=1in
fontsize: 11pt
output:
  pdf_document:
    toc: false
    df_print: kable
    fig_caption: false
    number_sections: false
    dev: pdf
    highlight: tango
  html_document:
    theme: default
    self_contained: true
    toc: false
    df_print: kable
    fig_caption: false
    number_sections: false
    smart: true
    dev: svg
---

```{r setup, include = FALSE}
# DO NOT ALTER THIS CHUNK
knitr::opts_chunk$set(
  echo = TRUE,
  eval = TRUE,
  fig.width = 5,
  fig.asp = 0.618,
  out.width = "70%",
  dpi = 120,
  fig.align = "center",
  cache = FALSE
)
is_pdf <- try (("pdf_document" %in% rmarkdown::all_output_formats(knitr::current_input())), silent=TRUE)
is_pdf <- (is_pdf == TRUE)
# Load required packages
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(broom))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(modelr))
suppressPackageStartupMessages(library(plotly))
suppressPackageStartupMessages(library(readxl))
suppressPackageStartupMessages(library(infer))

# Load dataset
Group_dataset <- read_xlsx("Group_dataset.xlsx")

```


#GHG = Greenhouse Gases
#FJO = Female Job Occupation
#YOY = Year-on-Year

#Outlier function
```{r}
find_outlier <- function(x) {
  return(x < quantile(x, .25) - 1.5*IQR(x) | x > quantile(x, .75) + 1.5*IQR(x))
}
```


# Organizing Dataset (Hyunwoo Kang)


## Summarize
```{r}
summary(Group_dataset)
```


# Select
```{r}
Envo_ft <- Group_dataset %>%
 select(Year, Birth_per_1000, Birth_YOY, GHG, GHG_YOY)
```

```{r}
Econ_ft <- Group_dataset %>%
  select(Year, Birth_per_1000, Birth_YOY, INF_Rate, Inflation_YOY)
```

```{r}
Soci_ft <- Group_dataset %>%
   select(Year, Birth_per_1000, Birth_YOY, FJO, FJO_YOY)
```


# Variation of Birth Rate change Year-on-Year (Hyunwoo Kang)

```{r}
 Group_dataset %>%
  ggplot() +
  geom_line(mapping = aes(y = Birth_YOY, x= Year)) +
  geom_point(mapping = aes(y = Birth_YOY, x= Year))+ 
  labs(title = "Change on Birth rate year-on-year", 
       y = "Birth Rate_YOY", 
       x = "Year")
```


```{r}
 Group_dataset %>%
  ggplot() +
  geom_point(mapping = aes(y = Birth_per_1000, x= Year))+ 
  geom_smooth(mapping = aes(y = Birth_per_1000, x = Year), method = "lm") +
  labs(title = "Change on Birth rate", 
       y = "Birth Rate (per 1000)", 
       x = "Year")
```




# Variation and Covariation - Envo_ft (Songlee Jun)

```{r}
 Group_dataset %>%
  ggplot() +
  geom_line(mapping = aes(y = GHG_YOY, x= Year)) +
  geom_point(mapping = aes(y = GHG_YOY, x= Year))+ 
  labs(title = "Change on Greenhouse Gas emission year-on-year", 
       y = "GHG_YOY", 
       x = "Year")
```
```{r}
Group_dataset %>%
  ggplot(mapping = aes(x = '', y = GHG_YOY)) +
  geom_boxplot(outlier.colour = "red", outlier.shape = 16) +
  stat_summary(
    aes(label = round(..y.., 1)),
    geom = "text",
    fun.data = function(y) {
      out <- boxplot.stats(y)$out
      if (length(out) == 0) return(NULL)
      data.frame(y = out)
    },
    hjust = -0.5
  ) +
  labs(
    title = "Greenhouse gas YOY Boxplot",
    y = "Greenhouse Gas Emission YOY"
  )

```

```{r}
Envo_ft %>%
 ggplot() +
 geom_point(mapping = aes(x = Year, y = GHG)) +
 geom_smooth(mapping = aes(x = Year, y = GHG), method = "lm") + 
  labs(title = "Change in Greenhouse Gas Emission",
       x = "Year",
       y = "Greenhouse gas emission")
```

```{r}
Group_dataset%>%
  pivot_longer(cols = c('Birth_YOY', 'GHG_YOY'),
               names_to = 'Comb_YOY',
               values_to = 'Val_YOY')%>%
  
ggplot(aes(y = Val_YOY, x = Year)) +
  geom_line(aes(color = Comb_YOY))+
  geom_point(aes(color = Comb_YOY)) +
  labs(title = "Greenhouse Gas Emission_YOY vs Birth rate_YOY",
    x = "Year",
    y = "YOY Value")
```
```{r}
Group_dataset %>%
  pivot_longer(cols = c('Birth_YOY', 'GHG_YOY'),
               names_to = 'Comb_YOY',
               values_to = 'Val_YOY') %>%
  
ggplot(aes(x = Val_YOY, fill = Comb_YOY)) +
  geom_histogram(position = 'dodge', bins = 30) +
  labs(title = "Distribution of Year-Over-Year Changes: 
       Greenhouse Gas Emission vs Birth Rate",
       x = "Year-Over-Year Change",
       y = "Frequency")
```

```{r}
Envo_ft %>%
   ggplot(mapping = aes(x = GHG, y = Birth_per_1000)) +
   geom_boxplot(outlier.colour = "red", outlier.shape = 16) +
   stat_summary(
     aes(label = round(..y.., 1)),
     geom = "text",
     fun.data = function(y) {
       out <- boxplot.stats(y)$out
       if(length(out) == 0) return(NULL)
       data.frame(y = out)
     },
     hjust = -0.5
   ) +
   labs(
     title = "Greenhouse gas emission vs Birth rate",
     x = 'Greenhouse gas emission',
     y = "Birth rate (per 1000)"
   )
```



```{r}
Envo_ft %>%
   ggplot()+
   geom_point(mapping = aes(x  = GHG, y = Birth_per_1000)) +
   geom_smooth(mapping = aes(x  = GHG, y  = Birth_per_1000), method="lm")+
  labs(
    title = "Greenhouse gas emission vs Birth rate",
    x = 'Greenhouse gas emission',
    y = "Birth rate (per 1000)")
```

```{r}
Group_dataset%>%
  pivot_longer(cols = c('Inflation_YOY', 'GHG_YOY'),
               names_to = 'Comb_YOY',
               values_to = 'Val_YOY')%>%
  
ggplot(aes(y = Val_YOY, x = Year)) +
  geom_line(aes(color = Comb_YOY))+
  geom_point(aes(color = Comb_YOY)) +
  labs(title = "Greenhouse Gas Emission_YOY vs Inflation Rate_YOY",
    x = "Year",
    y = "YOY Value") 
```
```{r}
Group_dataset %>%
  pivot_longer(cols = c('Inflation_YOY', 'GHG_YOY'),
               names_to = 'Comb_YOY',
               values_to = 'Val_YOY') %>%
  
ggplot(aes(x = Val_YOY, fill = Comb_YOY)) +
  geom_histogram(position = 'dodge', bins = 30) +
  labs(title = "Distribution of Year-Over-Year Changes:
       Greenhouse Gas Emission vs Inflation rate",
       x = "Year-Over-Year Change",
       y = "Frequency")
```

```{r}
Group_dataset %>%
   ggplot(mapping = aes(x = GHG, y = INF_Rate)) +
   geom_boxplot(outlier.colour = "red", outlier.shape = 16) +
   stat_summary(
     aes(label = round(..y.., 1)),
     geom = "text",
     fun.data = function(y) {
       out <- boxplot.stats(y)$out
       if (length(out) == 0) return(NULL)
       data.frame(y = out)
     },
     hjust = -0.5
   ) +
   labs(
     title = "Greenhouse gas emission vs Inflation rate",
     x = 'Greenhouse gas emission',
     y = "Inflation rate"
   )
```

```{r}
Group_dataset %>%
  ggplot() +
  geom_point(mapping = aes(x = GHG, y = INF_Rate))+
  geom_smooth(mapping = aes(x  = GHG, y  = INF_Rate), method="lm")+
  labs(
    title = "Greenhouse Gas Emission vs Inflation Rate",
    x = "Greenhouse gas emission",
    y = "Inflation rate") 
```



```{r}
Group_dataset%>%
  pivot_longer(cols = c('FJO_YOY', 'GHG_YOY'),
               names_to = 'Comb_YOY',
               values_to = 'Val_YOY')%>%
  
ggplot(aes(y = Val_YOY, x = Year)) +
  geom_line(aes(color = Comb_YOY))+
  geom_point(aes(color = Comb_YOY)) +
  labs(title = "Greenhouse Gas Emission_YOY vs Female Job
Occupation_YOY Line Graph",
    x = "Year",
    y = "YOY Values") 
```
```{r}
Group_dataset %>%
  pivot_longer(cols = c('FJO_YOY', 'GHG_YOY'),
               names_to = 'Comb_YOY',
               values_to = 'Val_YOY') %>%
  
ggplot(aes(x = Val_YOY, fill = Comb_YOY)) +
  geom_histogram(position = 'dodge', bins = 30) +
  labs(title = "Distribution of Year-Over-Year Changes:
       GHG Emission vs Female Job Occupancy",
       x = "Year-Over-Year Change",
       y = "Frequency")
```

```{r}
Group_dataset %>%
   ggplot(mapping = aes(x = GHG, y = FJO)) +
   geom_boxplot(outlier.colour = "red", outlier.shape = 16) +
   stat_summary(
     aes(label = round(..y.., 1)),
     geom = "text",
     fun.data = function(y) {
       out <- boxplot.stats(y)$out
       if (length(out) == 0) return(NULL)
       data.frame(y = out)
     },
     hjust = -0.5
   ) +
   labs(
     title = "Greenhouse gas emission vs Female Job Occupancy ",
     x = 'Greenhouse gas emission',
     y = "Female Job Occupancy"
   )
```


```{r}
Group_dataset%>%
  ggplot() +
  geom_point(mapping = aes(x = GHG, y = FJO)) +
geom_smooth(mapping=aes(x = GHG, y = FJO), method="lm")+
  labs(
    title = "Greenhouse Gas Emission vs Female Job
Occupation",
    x = "Greenhouse gas emission",
    y = "Female Job Occupation") 
```

# Modeling & Hyphothesis test- Envo_ft year-on-year (Byungwook Oh)

```{r}
# Model
Envo_ft_model <- lm(Birth_YOY ~ GHG_YOY, data = Envo_ft)
```

```{r}
# Tidy model
Envo_ft_model %>%
  tidy()
```

```{r}
# Null distribution
Envo_null_distribution <- Envo_ft %>%
  specify(Birth_YOY ~ GHG_YOY) %>%
  hypothesize(null="independence") %>%
  generate(reps=10000, type="permute") %>%
  calculate(stat="slope")
```

```{r}
# Observed stat
Observed_stat <- Envo_ft %>%
  specify(Birth_YOY ~ GHG_YOY) %>%
  calculate(stat="slope")
```

```{r}
# P-value
Envo_null_distribution %>%
  get_p_value(obs_stat=Observed_stat, direction="both")
```

```{r}
# P-value visualization
Envo_null_distribution %>%
  visualize() +
  shade_p_value(obs_stat=Observed_stat, direction= "both") +
  labs(title = "P-value Visualization")
```

# Modeling & Hyphothesis test- Envo_ft with actual value (Byungwook Oh)

```{r}
# Model
Envo_ft_model <- lm(Birth_per_1000 ~ GHG, data = Envo_ft)
```

```{r}
# Null distribution
Envo_null_distribution_rv <- Envo_ft %>%
  specify(Birth_per_1000 ~ GHG) %>%
  hypothesize(null="independence") %>%
  generate(reps=10000, type="permute") %>%
  calculate(stat="slope")
```

```{r}
# Observed stat
Observed_stat <- Envo_ft %>%
  specify(Birth_per_1000 ~ GHG) %>%
  calculate(stat="slope")
```

```{r}
# P-value
Envo_null_distribution_rv %>%
  get_p_value(obs_stat=Observed_stat, direction="both")
```
```{r}
# P-value visualization
Envo_null_distribution_rv %>%
  visualize() +
  shade_p_value(obs_stat=Observed_stat, direction= "both") +
  labs(title = "P-value Visualization")
```


# Variation and Covariation - Econ_ft (Dawon Kyoung)


```{r}
 Group_dataset %>%
  ggplot() +
  geom_line(mapping = aes(y = Inflation_YOY, x= Year)) +
  geom_point(mapping = aes(y = Inflation_YOY, x= Year))+ 
  labs(title = "Change on Inflation rate year-on-year",
       y = "Inflation rate_YOY", x = "Year")
```
```{r}
Group_dataset %>%
  ggplot(mapping = aes(x = '', y = Inflation_YOY)) +
  geom_boxplot(outlier.colour = "red", outlier.shape = 16) +
  stat_summary(
    aes(label = round(..y.., 1)),
    geom = "text",
    fun.data = function(y) {
      out <- boxplot.stats(y)$out
      if (length(out) == 0) return(NULL)
      data.frame(y = out)
    },
    hjust = -0.5
  ) +
  labs(
    title = "Inflation rate YOY Boxplot",
    y = "Inflation YOY"
  )

```

```{r}
 Econ_ft %>%
  ggplot() +
  geom_point(mapping = aes(y = INF_Rate, x= Year))+ 
  geom_smooth(mapping = (aes(y = INF_Rate, x = Year)), method ='lm') +
  labs(title = "Change in Inflation rate", 
       y = "Inflation Rate", 
       x = "Year")
```


```{r}
Group_dataset%>%
  pivot_longer(cols = c('Inflation_YOY', 'Birth_YOY'),
               names_to = 'Comb_YOY',
               values_to = 'Val_YOY')%>%
  
ggplot(aes(y = Val_YOY, x = Year)) +
  geom_line(aes(color = Comb_YOY))+
  geom_point(aes(color = Comb_YOY)) +
  labs(
    title= 'Inflation rate_YOY vs Birth rate_YOY',
    x= 'Year',
    y= "YOY Value")
```
```{r}
Group_dataset %>%
  pivot_longer(cols = c('Inflation_YOY', 'Birth_YOY'),
               names_to = 'Comb_YOY',
               values_to = 'Val_YOY') %>%
  
ggplot(aes(x = Val_YOY, fill = Comb_YOY)) +
  geom_histogram(position = 'dodge', bins = 30) +
  labs(title = "Distribution of Year-Over-Year Changes:
       Inflation Rate vs Birth Rate",
       x = "Year-Over-Year Change",
       y = "Frequency")
```

```{r}
Econ_ft %>%
   ggplot(mapping = aes( x = INF_Rate, y = Birth_per_1000)) +
   geom_boxplot(outlier.colour = "red", outlier.shape = 16) +
   stat_summary(
     aes(label = round(..y.., 1)),
     geom = "text",
     fun.data = function(y) {
       out <- boxplot.stats(y)$out
       if (length(out) == 0) return(NULL)
       data.frame(y = out)
     },
     hjust = -0.5
   ) +
  labs(
    title = "Inflation rate vs Birth Rate",
    x = 'Inflation rate',
    y = "Birth Rate")
```

```{r}
Econ_ft %>%
  ggplot() +
  geom_point(mapping=aes(x = INF_Rate, y = Birth_per_1000)) + 
  geom_smooth(mapping = aes(x = INF_Rate, y = Birth_per_1000), method = 'lm') +
  labs(
    title= 'Inflation rate vs Birth rate',
    x= 'Inflation rate',
    y= "Birth rate (per 1000)")
```


```{r}
Group_dataset%>%
  pivot_longer(cols = c('Inflation_YOY', 'GHG_YOY'),
               names_to = 'Comb_YOY',
               values_to = 'Val_YOY')%>%
  
ggplot(aes(y = Val_YOY, x = Year)) +
  geom_line(aes(color = Comb_YOY))+
  geom_point(aes(color = Comb_YOY)) +
   labs(
     title= 'Inflation rate_YOY vs Greenhouse Gas Emission_YOY',
     x= 'Year',
     y= 'YOY values')
```
```{r}
Group_dataset %>%
  pivot_longer(cols = c('Inflation_YOY', 'GHG_YOY'),
               names_to = 'Comb_YOY',
               values_to = 'Val_YOY') %>%
  
ggplot(aes(x = Val_YOY, fill = Comb_YOY)) +
  geom_histogram(position = 'dodge', bins = 30) +
  labs(title = "Distribution of Year-Over-Year Changes:
       Inflation Rate vs Greenhouse Gas Emission",
       x = "Year-Over-Year Change",
       y = "Frequency")
```

```{r}
Group_dataset %>%
   ggplot(mapping = aes(x = INF_Rate, y = GHG)) +
   geom_boxplot(outlier.colour = "red", outlier.shape = 16) +
   stat_summary(
     aes(label = round(..y.., 1)),
     geom = "text",
     fun.data = function(y) {
       out <- boxplot.stats(y)$out
       if (length(out) == 0) return(NULL)
       data.frame(y = out)
     },
     hjust = -0.5
   ) +
  labs(
    title = "Inflation rate vs Greenhouse gas emission",
    x = 'Inflation rate',
    y = "Greenhouse gas emission")
```

```{r}
Group_dataset %>%
   ggplot() +
   geom_point(mapping= aes( x = INF_Rate, y = GHG))+
   geom_smooth(mapping=aes(x = INF_Rate, y = GHG),
method= 'lm')+
   labs(
     title= 'Inflation rate vs Greenhouse Gas Emission',
     x= 'Inflation rate',
     y= 'Greenhouse Gas Emission')
```


```{r}
Group_dataset %>%
  pivot_longer(cols = c('Inflation_YOY', 'FJO_YOY'),
               names_to = 'Comb_YOY',
               values_to = 'Val_YOY')%>%
  
ggplot(aes(x = Year, y = Val_YOY)) +
   geom_line(aes(color = Comb_YOY))+
   geom_point(aes(color = Comb_YOY)) +
   labs(
     title = 'Inflation rate_YOY vs Female Job Occupation_YOY',
     x = 'Year',
     y = 'YOY Values')

```

```{r}
Group_dataset %>%
  pivot_longer(cols = c('FJO_YOY', 'Inflation_YOY'),
               names_to = 'Comb_YOY',
               values_to = 'Val_YOY') %>%
  
ggplot(aes(x = Val_YOY, fill = Comb_YOY)) +
  geom_histogram(position = 'dodge', bins = 30) +
  labs(title = "Distribution of Year-Over-Year Changes:
       Inflation Rate vs Female Job Occupancy",
       x = "Year-Over-Year Change",
       y = "Frequency")
```

```{r}
Group_dataset %>%
   ggplot(mapping = aes(x = INF_Rate, y = FJO)) +
   geom_boxplot(outlier.colour = "red", outlier.shape = 16) +
   stat_summary(
     aes(label = round(..y.., 1)),
     geom = "text",
     fun.data = function(y) {
       out <- boxplot.stats(y)$out
       if (length(out) == 0) return(NULL)
       data.frame(y = out)
     },
     hjust = -0.5
   ) +
  labs(
    title = "Inflation rate vs Female Job Occupancy ",
    x = 'Inflation rate',
    y = "Female Job Occupancy")
```


```{r}
Group_dataset %>%
   ggplot() +
   geom_point(mapping = aes(x= INF_Rate, y= FJO))+
   geom_smooth(mapping=aes(x= INF_Rate, y= FJO),
method= 'lm')+
   labs(
     title= 'Inflation rate vs Female Job Occupation',
     x= 'Inflation rate',
     y= 'Female Job Occupation')
```

# Modeling & Hyphothesis test- Econ_ft year on year (Daeun Choi)

```{r}
# Model
Econ_ft_model <- lm(Birth_YOY ~ Inflation_YOY, data=Econ_ft)
```

```{r}
# Tidy model
Econ_ft_model %>%
  tidy()
```

```{r}
# Null distribution
Econ_null_distribution <- Econ_ft %>%
  specify(Birth_YOY ~ Inflation_YOY) %>%
  hypothesize(null="independence") %>%
  generate(reps=10000, type="permute") %>%
  calculate(stat="slope")
```

```{r}
# Observed stat
Observed_stat <- Econ_ft %>%
  specify(Birth_YOY ~ Inflation_YOY) %>%
  calculate(stat="slope")
```

```{r}
# P-value
Econ_null_distribution %>%
  get_p_value(obs_stat=Observed_stat, direction="both")
```

```{r}
# P-value visualization
Econ_null_distribution %>%
  visualize() +
  shade_p_value(obs_stat=Observed_stat, direction= "both") +
  labs(title = "P-value Visualization")
```

# Modeling & Hypothesis test - Econ_ft with actual value (Daeun Choi)

```{r}
# Model
Econ_ft_model <- lm(Birth_per_1000 ~ INF_Rate, data = Econ_ft)
```

```{r}
# Null distribution
Econ_null_distribution_rv <- Econ_ft %>%
  specify(Birth_per_1000 ~ INF_Rate) %>%
  hypothesize(null="independence") %>%
  generate(reps=10000, type="permute") %>%
  calculate(stat="slope")
```

```{r}
# Observed stat
Observed_stat <- Econ_ft %>%
  specify(Birth_per_1000 ~ INF_Rate) %>%
  calculate(stat="slope")
```

```{r}
# P-value
Econ_null_distribution_rv %>%
  get_p_value(obs_stat=Observed_stat, direction="both")
```

```{r}
# P-value visualization
Econ_null_distribution_rv %>%
  visualize() +
  shade_p_value(obs_stat=Observed_stat, direction= "both") +
  labs(title = "P-value Visualization")
```


# Variation and Covariation - Soci_ft (Eunho Cha)

```{r}
 Group_dataset %>%
  ggplot() +
  geom_line(mapping = aes(y = FJO_YOY, x= Year)) +
  geom_point(mapping = aes(y = FJO_YOY, x= Year))+ 
  labs(title = "Change on Female Job Occupation year-on-year", 
       y = "FJO_YOY", 
       x = "Year")
```
```{r}
Group_dataset %>%
   ggplot(mapping = aes(x = '', y = FJO_YOY)) +
   geom_boxplot(outlier.colour = "red", outlier.shape = 16) +
   stat_summary(
     aes(label = round(..y.., 1)),
     geom = "text",
     fun.data = function(y) {
       out <- boxplot.stats(y)$out
       if (length(out) == 0) return(NULL)
       data.frame(y = out)
     },
     hjust = -0.5
   ) +
  labs(
    title = "Female job Occupancy YOY Boxplot",
    y = "Female Job Occupancy YOY")
```

```{r}  
Soci_ft %>%
  ggplot() +
  geom_point(mapping = aes(y = FJO, x = Year)) +
  geom_smooth(mapping = aes(y = FJO, x = Year), method = 'lm') +
  labs(title = "Change in Female Job Occupation",
       y  = "Female Job Occupation",
       x = "Year")
```


```{r}
Group_dataset%>%
  pivot_longer(cols = c('FJO_YOY', 'Birth_YOY'),
               names_to = 'Comb_YOY',
               values_to = 'Val_YOY')%>%
  
ggplot(aes(y = Val_YOY, x = Year)) +
  geom_line(aes(color = Comb_YOY))+
  geom_point(aes(color = Comb_YOY)) +
   labs(
     title="Female Job Occupation_YOY vs Birth Rate_YOY",
     x= "Year",
     y= "YOY Values"
   )
```


```{r}
Group_dataset %>%
  pivot_longer(cols = c('FJO_YOY', 'Birth_YOY'),
               names_to = 'Comb_YOY',
               values_to = 'Val_YOY') %>%
  
ggplot(aes(x = Val_YOY, fill = Comb_YOY)) +
  geom_histogram(position = 'dodge', bins = 30) +
  labs(title = "Distribution of Year-Over-Year Changes:
       Female Job Occupancy vs Birth rate",
       x = "Year-Over-Year Change",
       y = "Frequency")
```


```{r}
Group_dataset %>%
   ggplot(mapping = aes(x = FJO, y = Birth_per_1000)) +
   geom_boxplot(outlier.colour = "red", outlier.shape = 16) +
   stat_summary(
     aes(label = round(..y.., 1)),
     geom = "text",
     fun.data = function(y) {
       out <- boxplot.stats(y)$out
       if (length(out) == 0) return(NULL)
       data.frame(y = out)
     },
     hjust = -0.5
   ) +
  labs(
    title = "Female job Occupancy vs Birth Rate",
    x = 'Female Job Occupancy',
    y = "Birth Rate")
```


```{r}
Soci_ft %>%
   ggplot() +
   geom_point(mapping = aes(x= FJO, y= Birth_per_1000))+
   geom_smooth(mapping=aes(x = FJO, y = Birth_per_1000), method="lm")+
   labs(
     title="Female Job Occupation vs Birth Rate",
     x= "Female Job Occupation",
     y= "Birth Rate (per 1000)"
   )
```


```{r}
Group_dataset%>%
  pivot_longer(cols = c('FJO_YOY', 'GHG_YOY'),
               names_to = 'Comb_YOY',
               values_to = 'Val_YOY')%>%
  
ggplot(aes(y = Val_YOY, x = Year)) +
  geom_line(aes(color = Comb_YOY))+
  geom_point(aes(color = Comb_YOY)) +
   labs(
     title= "Female Job Occupation_YOY vs 
     Greenhouse Gas Emission_YOY",
     x= "Year",
     y= "YOY Values"
   )
```

```{r}
Group_dataset %>%
  pivot_longer(cols = c('FJO_YOY', 'GHG_YOY'),
               names_to = 'Comb_YOY',
               values_to = 'Val_YOY') %>%
  
ggplot(aes(x = Val_YOY, fill = Comb_YOY)) +
  geom_histogram(position = 'dodge', bins = 30) +
  labs(title = "Distribution of Year-Over-Year Changes:
       Female Job Occupancy vs Greenhouse Gas Emission",
       x = "Year-Over-Year Change",
       y = "Frequency")
```
```{r}
Group_dataset %>%
   ggplot(mapping = aes(x = FJO, y = GHG)) +
   geom_boxplot(outlier.colour = "red", outlier.shape = 16) +
   stat_summary(
     aes(label = round(..y.., 1)),
     geom = "text",
     fun.data = function(y) {
       out <- boxplot.stats(y)$out
       if (length(out) == 0) return(NULL)
       data.frame(y = out)
     },
     hjust = -0.5
   ) +
    labs(
     title= "Female Job Occupation vs Greenhouse Gas Emission",
     x= "Female Job Occupation",
     y= "Greenhouse Gas Emission"
    )
```


```{r}
Group_dataset %>%
   ggplot() +
   geom_point(mapping= aes (x= FJO, y= GHG)) +
   geom_smooth(mapping=aes (x= FJO, y=GHG), method="lm")+
   labs(
     title= "Female Job Occupation vs Greenhouse Gas Emission",
     x= "Female Job Occupation",
     y= "Greenhouse Gas Emission"
   )
```


```{r}
Group_dataset%>%
  pivot_longer(cols = c('FJO_YOY', 'Inflation_YOY'),
               names_to = 'Comb_YOY',
               values_to = 'Val_YOY')%>%
  
ggplot(aes(y = Val_YOY, x = Year)) +
  geom_line(aes(color = Comb_YOY))+
  geom_point(aes(color = Comb_YOY)) +
   labs(
     title= "Female Job Occupation_YOY vs Inflation Rate_YOY",
     x= "Year",
     y= "YOY Values"
   )
``` 


```{r}
Group_dataset %>%
  pivot_longer(cols = c('FJO_YOY', 'Inflation_YOY'),
               names_to = 'Comb_YOY',
               values_to = 'Val_YOY') %>%
  
ggplot(aes(x = Val_YOY, fill = Comb_YOY)) +
  geom_histogram(position = 'dodge', bins = 30) +
  labs(title = "Distribution of Year-Over-Year Changes:
       Female Job Occupancy vs Inflation Rate",
       x = "Year-Over-Year Change",
       y = "Frequency")
```


```{r}
Group_dataset %>%
   ggplot(mapping = aes(x = FJO, y = INF_Rate)) +
   geom_boxplot(outlier.colour = "red", outlier.shape = 16) +
   stat_summary(
     aes(label = round(..y.., 1)),
     geom = "text",
     fun.data = function(y) {
       out <- boxplot.stats(y)$out
       if (length(out) == 0) return(NULL)
       data.frame(y = out)
     },
     hjust = -0.5
   ) +
    labs(
     title= "Female Job Occupation vs Inflation Rate",
     x= "Female Job Occupation",
     y= "Inflation Rate"
    )
```


```{r}
Group_dataset %>%
   ggplot() +
   geom_point(mapping= aes (x= FJO, y=INF_Rate)) +
   geom_smooth(mapping=aes (x= FJO, y=INF_Rate), method="lm")+
   labs(
     title= "Female Job Occupation vs Inflation Rate",
     x= "Female Job Occupation",
     y= "Inflation Rate"
   )
```


# Modeling & Hypothesis test - Soci_ft year on year (Duy Tran)

```{r}
# Model
Soci_ft_model <- lm(Birth_YOY ~ FJO_YOY, data = Soci_ft)
```

```{r}
# Tidy model
Soci_ft_model %>%
  tidy()
```

```{r}
# Null distribution
Soci_null_distribution <- Soci_ft %>%
  specify(Birth_YOY ~ FJO_YOY) %>%
  hypothesize(null="independence") %>%
  generate(reps=10000, type="permute") %>%
  calculate(stat="slope")
```

```{r}
# Observed stat
Observed_stat <- Soci_ft %>%
  specify(Birth_YOY ~ FJO_YOY) %>%
  calculate(stat="slope")
```

```{r}
# P-value
Soci_null_distribution %>%
  get_p_value(obs_stat=Observed_stat, direction="both")
```

```{r}
# P-value visualization
Soci_null_distribution %>%
  visualize() +
  shade_p_value(obs_stat=Observed_stat, direction="both") +
  labs(title ="P-value visualization")
```

# Modeling & Hyphothesis test- Soci_ft with actual value (Duy Tran)

```{r}
# Model
Soci_ft_model <- lm(Birth_per_1000 ~ FJO, data = Soci_ft)
```

```{r}
# Null distribution
Soci_null_distribution_rv <- Soci_ft %>%
  specify(Birth_per_1000 ~ FJO) %>%
  hypothesize(null="independence") %>%
  generate(reps=10000, type="permute") %>%
  calculate(stat="slope")
```

```{r}
# Observed stat
Observed_stat <- Soci_ft %>%
  specify(Birth_per_1000 ~ FJO) %>%
  calculate(stat="slope")
```

```{r}
# P-value
Soci_null_distribution_rv %>%
  get_p_value(obs_stat=Observed_stat, direction="both")
```

```{r}
# P-value visualization
Soci_null_distribution_rv %>%
  visualize() +
  shade_p_value(obs_stat=Observed_stat, direction= "both") +
  labs(title = "P-value Visualization")
```



